Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-06-22 paper/paper1/ms.tex
Fill in placeholder text with some numbers on telluric lines.

The number of pixels in the telluric model can be chosen at the time of running a \texttt{TelFit} model.  Here we choose a spectral resolution \censorbox{$R\sim1\times10^6$}, adequate for resolving telluric lines, and yielding \censorbox{xx} pixels across the HPF bandwidth.  This pixel sampling is slightly \censorbox{finer} than the native PHOENIX pixel sampling.  The number of telluric lines depends on the atmospheric properties, in particular the Earth surface temperature and relative humidity $RH$.  For a \censorbox{T=x}, \censorbox{RH=y}, we detect \censorbox{zz} telluric lines across the entire HPF bandwidth.

>>>>

The number of pixels in the telluric model can be chosen at the time of running a \texttt{TelFit} model.  Here we choose a spectral resolution $R\sim10^6$, adequate for resolving narrow telluric lines, and yielding about 2 million pixels across the entire HPF bandwidth.  This pixel sampling is about $6\times$ finer than the native PHOENIX pixel sampling.  The number of telluric lines depends on the atmospheric properties, in particular the Earth surface temperature and relative humidity $RH$.  For a surface temperature of $T=290 K\; (62^\circ~F)$, a relative humidity of 40\%, and typical conditions for McDonald Observatory, we anticipate 3615 telluric lines across the entire HPF bandwidth.
